
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Runchao Han} % Your name
\address{20 Exhibition Walk, Clayton VIC 3800, Australia} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{runchao.han@monash.edu \\ \url{https://runchao.rocks}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    {\bf Monash University and CSIRO-Data61} \hfill {\em February 2019 - August 2022 (expected)}
    \\ Doctor of Philosophy\hfill { Supervisors: Jiangshan Yu, Joseph Liu and Shiping Chen}
    \\ Department of Software Systems and Cybersecurity\\
    %
    \\{\bf The University of Manchester} \hfill {\em August 2017 - September 2018}
    \\ MSc Advanced Computer Science (with Distinction)\hfill {Supervisor: Christos Kotselidis}
    \\ School of Computer Science\hfill { Overall Percentage: 82/100 }\\
    %
    \\{\bf Beijing University of Posts and Telecommunications} \hfill {\em September 2013 - July 2017}
    \\ BSc E-Commerce Engineering with Law\hfill { Overall Percentage: 83/100 }
    %Minor in Linguistics \smallskip \\
    %Member of Eta Kappa Nu \\
    %Member of Upsilon Pi Epsilon \\


\end{rSection}

% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Research and impact}
    I'm broadly interested in distributed systems security.
    My current research focuses on designing secure and scalable Blockchains and decentralised protocols (e.g., Decentralised Randomness Beacon).
    My research applies techniques from Cryptography and Distributed Computing.

    My research has led to real-world impacts and media coverage. For example,
    \begin{itemize}
        \item I invented \textsc{RandChain} [HYL20], a new family of Decentralised Randomness Beacon protocols that are simple, secure and scalable. This research is featured in \href{https://vdfresearch.org/}{VDF Research} and was presented at \href{https://decrypto.org/seminar/}{Decrypto seminar series}.
        \item My paper analysing \emph{shard allocation} (a key component and a missing abstraction in sharded blockchains) [HYZ20] is selected as \href{https://zkcapital.substack.com/}{"Paper of the Week" (Issue \#68)} by ZK Capital.
        \item I studied two overlooked 51\% attacks on PoW-based blockchains [HSY+20]. Three large-scale 51\% attacks on Ethereum Classic (\href{https://news.bitcoin.com/ethereum-classic-suffers-51-attack-again-delisting-risk-amplified}{1},\href{https://decrypt.co/40196/hackers-launch-third-51-attack-on-ethereum-classic-this-month}{2},\href{https://coingeek.com/over-1m-double-spent-in-latest-ethereum-classic-51-attack}{3}) happened within a month are likely to be our analysed attacks.
        \item I identified and formalised an overlooked design flaw of the Atomic Swap protocol [HLY19]. The flaw allows the swap initiator to arbitrage, making the protocol unfair. Our proposed fixes are standardised as an Ethereum Improvement Proposal (\href{https://github.com/ethereum/EIPs/issues/2266}{EIP-2266}). This research is covered by \href{https://cryptonews.com.au/monash-university-researchers-developing-cryptocurrency-transaction-platform}{CryptoNews} and \href{https://www.monash.edu/blockchain/news/to-realise-their-potential,-business-blockchains-must-learn-to-communicate}{Monash University}, and was presented at \href{https://www.youtube.com/watch?v=wwWcfl9N65k}{Peep an EIP series \#23}.
        \item I conducted the first performance analysis on memory-hard mining algorithms [HFK19]. This research is nominated for the best paper at ISPASS'19 and is covered by \href{https://medium.com/@horizonfintex/blockchain-research-bytes-1-9d023e080765}{Horizon Globex}.
    \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Publications}

    Publication list can also be found at \href{https://dblp.org/pers/hd/h/Han:Runchao}{DBLP} and \href{http://scholar.google.com/citations?user=xbpDocQAAAAJ&hl=en}{Google Scholar}.
    All of my papers are available online, and most of them are hosted on \href{https://eprint.iacr.org/}{IACR ePrint}.

    \begin{itemize}
        \item[\href{https://eprint.iacr.org/2020/1033}{HYL+20}] On the Security and Performance of Blockchain Sharding. Runchao Han, Jiangshan Yu, Haoyu Lin, Shiping Chen, Paulo Esteves-Veríssimo. \textbf{In submission}.
        \item[\href{https://eprint.iacr.org/2020/1033}{HYL20}] \textsc{RandChain}: Decentralised Randomness Beacon from Sequential Proof-of-Work. Runchao Han, Jiangshan Yu, Haoyu Lin. \textbf{In submission}.
        \item[\href{https://eprint.iacr.org/2020/943}{HYZ20}] Analysing and Improving Shard Allocation Protocols for Sharded Blockchains. Runchao Han, Jiangshan Yu, Ren Zhang. \textbf{In submission}.
        \item[\href{https://eprint.iacr.org/2020/456.pdf}{LHY20}] General Congestion Attack on HTLC-Based Payment Channel Networks. Zhichun Lu, Runchao Han, Jiangshan Yu. The 3rd International Conference on Blockchain Economics, Security and Protocols \textbf{(Tokenomics'21)}.
        \item[\href{https://eprint.iacr.org/2019/752}{HSY+20}] Fact and Fiction: Challenging the honest majority assumption of permissionless blockchains. Runchao Han, Zhimei Sui, Jiangshan Yu, Joseph Liu, Shiping Chen. The 16th ACM ASIA Conference on Computer and Communications Security \textbf{(AsiaCCS'21)}.
        \item[\href{https://github.com/DEX-ware/vrf-mining/blob/master/paper/main.pdf}{HYL20a}] VRF-based mining: Simple Non-outsourceable Cryptocurrency Mining. Runchao Han, Haoyu Lin, Jiangshan Yu. The 4th International Workshop on Cryptocurrencies and Blockchain Technology, in conjunction with the 25th European Symposium on Research in Computer Security \textbf{(CBT@ESORICS'20)}.
        \item[\href{https://eprint.iacr.org/2019/896}{HLY19}] On the optionality and fairness of Atomic Swaps. Runchao Han, Haoyu Lin, Jiangshan Yu.  ACM Conference on Advances in Financial Technologies \textbf{(AFT'19)}.
        \item[\href{https://www.research.manchester.ac.uk/portal/files/85753741/paper.pdf}{HFK19}] Demystifying Crypto Mining: Performance Analysis and Optimizations of PoW Algorithms. Runchao Han, Nikolaos Foutris, Christos Kotselidis. IEEE International Symposium on Performance Analysis of Systems and Software \textbf{(ISPASS'19, best paper nominee)}.
        \item[\href{https://gramoli.redbellyblockchain.io/web/doc/pubs/IoT2019.pdf}{HSGX19}] On the performance of distributed ledgers for internet of things. Runchao Han, Gary Shapiro, Vincent Gramoli, Xiwei Xu. Internet of Things; Engineering Cyber Physical Human Systems \textbf{(Elsevier IoT'19)}.
        \item[\href{https://www.researchgate.net/profile/Runchao_Han/publication/331227984_Evaluating_CryptoNote-Style_Blockchains_14th_International_Conference_Inscrypt_2018_Fuzhou_China_December_14-17_2018_Revised_Selected_Papers/links/5c747901299bf1268d25a5f5/Evaluating-CryptoNote-Style-Blockchains-14th-International-Conference-Inscrypt-2018-Fuzhou-China-December-14-17-2018-Revised-Selected-Papers.pdf}{HYLZ18}] Evaluating CryptoNote-Style Blockchains. Runchao Han, Jiangshan Yu, Joseph Liu, Peng Zhang. International Conference on Information Security and Cryptology \textbf{(Inscrypt'18)}.
        \item[\href{https://gramoli.redbellyblockchain.io/web/doc/pubs2/blockchain-iot.pdf}{HGX18}] Evaluating Blockchains for IoT. Runchao Han, Vincent Gramoli, Xiwei Xu. The 9th IFIP International Conference on New Technologies, Mobility and Security \textbf{(NTMS'18)}.
    \end{itemize}
\end{rSection}

\begin{rSection}{Talks}
    \begin{itemize}
        \item Fact and Fiction: Challenging the honest majority assumption of permissionless blockchains. AsiaCCS conference (virtual). June, 2021.
        \item RandChain: Decentralised Randomness Beacon from Sequential Proof-of-Work. Seminar at Decrypto. November, 2020.
        \item VRF-Based Mining: Simple Non-Outsourceable Cryptocurrency Mining. CBT@ESORICS workshop. September, 2020.
        \item Demystifying Crypto-Mining: Analysis and Optimizations of Memory-Hard PoW Algorithms. Seminar at Huawei Noah's Ark Lab. July, 2020.
        \item On the optionality and fairness of Atomic Swaps.
              \begin{itemize}
                  \item Peep an EIP \#23: EIP-2266. February, 2021.
                  \item AFT conference at Zurich. October, 2019.
              \end{itemize}
    \end{itemize}
\end{rSection}


\begin{rSection}{Teaching}
    \begin{itemize}
        \item Teaching associate for FIT 5214 Blockchain, Monash University. 2019 Fall.
    \end{itemize}
\end{rSection}


\begin{rSection}{Professional services}
    \subsection*{(External) reviewer}
    \begin{itemize}
        \item 2022: EuroS\&P
        \item 2021: DSN, ICBC, IEEE Blockchain, NSS, MSN, TrustCom, IEEE Trans.\ of Service Computing
        \item 2020: AFT, ICDCS, SRDS, ACNS, AsiaCCS, TrustCom, ACISP, ICBC, TDSC, The Computer Journal, IEEE IoT Journal, IEEE Software Journal, IEEE Trans.\ of Service Computing
        \item 2019: Indocrypt, TrustCom, Future Generation Computing System
    \end{itemize}
\end{rSection}

% \begin{rSection}{Work experience}

%     \begin{rSubsubsection}{Bytom Blockchain}{September 2018 - January 2019}{Intern Blockchain Engineer}{Hangzhou, China}
%     \end{rSubsubsection}

%     \begin{rSubsubsection}{CNIC, Chinese Academy of Sciences}{June 2017 - July 2017}{Intern Researcher}{Beijing, China}
%     \end{rSubsubsection}

% \end{rSection}

\begin{rSection}{Additional Information}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Membership & Association for Computing Machinery (ACM, student member)                \\
                   & Institute of Electrical and Electronics Engineers (IEEE, student member) \\
                   & USENIX Association (USENIX)                                              \\
                   & International Association for Cryptologic Research (IACR)                \\
        LinkedIn   & runchao-han                                                              \\
        Github     & SebastianElvis                                                           \\
        Wechat     & elvisage                                                                 \\
        References & Available upon request
    \end{tabular}

\end{rSection}

\end{document}
